---
title: "pums analysis, multi weeks"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = TRUE,
	dpi = 300
)
```

```{r}
library(tidyverse)
library(srvyr)
library(rvest)
library(rcartocolor)
library(ggalluvial)
```

# functions & cleanup

```{r}
survey_share_by <- function(srvy, ..., .add, digits = 2, vartype = "se") {
  grp_vars <- quos(...)
  # dplyr has moved to .add, but srvyr not updated yet
  srvy %>%
    group_by(!!!grp_vars, add = .add) %>%
    summarise(share = survey_mean(vartype = vartype, level = 0.9)) %>%
    mutate_at(vars(matches("share")), signif, digits = digits)
}

compare_share <- function(srvy_lst, ..., .add = TRUE) {
  srvy_lst %>%
    map_dfr(survey_share_by, ..., .add = .add, .id = "name") %>%
    mutate(name = as_factor(name) %>% fct_relabel(toupper))
}

compare_grps <- function(srvy_list = srvys, col, total = TRUE, gender = TRUE, age_range = TRUE, race = TRUE, hh_income = TRUE, kids_present = TRUE) {
  # still kinda redundant
  filtered <- srvy_list %>%
    map(filter, !is.na({{ col }}))
  
  out <- list()
  
  if (total) out$total <- compare_share(filtered, total = "total", {{ col }})
  if (gender) out$by_gender <- compare_share(filtered, gender, {{ col }})
  if (age_range) out$by_age <- compare_share(filtered, age_range, {{ col }})
  if (race) out$by_race <- compare_share(filtered, race, {{ col }})
  if (hh_income) out$by_income <- compare_share(filtered, hh_income, {{ col }})
  if (kids_present) out$by_kids <- compare_share(filtered, kids_present, {{ col }})
  
  out
}

combine_dimensions <- function(dfs, ...) {
  drop_vars <- quos(...)
  dfs %>%
    map(ungroup) %>%
    # map(select, -{{ drop_col }}, -share_se) %>%
    map_dfr(pivot_longer, -c(name, starts_with("share"), !!!drop_vars), names_to = "dimension", values_to = "group",
            names_ptypes = list(dimension = factor())) %>%
    filter(!is.na(group)) %>%
    mutate(group = as_factor(ifelse(group == "total", as.character(name), as.character(group))))
}

theme_set(theme_minimal())
```



```{r}
week_dates <- read_html("https://www.census.gov/programs-surveys/household-pulse-survey/datasets.html") %>%
  html_nodes("h4.uscb-h4") %>%
  html_text() %>%
  str_match_all("([A-Z][a-z]+ \\d{1,2})") %>%
  map(~.[, 1]) %>%
  rev() %>%
  map(paste, "2020") %>%
  map(lubridate::mdy) %>%
  map(enframe, name = "pt", value = "date") %>%
  map_dfr(mutate, pt = fct_recode(as.character(pt), start = "1", end = "2"), .id = "week") %>%
  pivot_wider(names_from = pt, names_glue = "{pt}_{.value}", values_from = date) %>%
  mutate(week = as.numeric(week))
```


```{r}
all_pums <- list.files(here::here("fetch_data/microdata"), full.names = TRUE) %>%
  map(readRDS)

pums_df <- all_pums %>% 
  map(janitor::clean_names) %>%
  map_dfr(select, scram, state = est_st, week, pweight, birth_year = tbirth_year, gender = egender, rhispanic, rrace, hh_income = income, nkids = thhld_numkid, wrkloss, prior_food = prifoodsuf, current_food = curfoodsuf, delay_care = delay, miss_care = notget, anxious, tenure, last_housing = mortlmth, housing_conf = mortconf, internet = intrntavail, starts_with("foodsufr"), freefood, starts_with("wherefree")) %>%
  mutate_at(vars(-scram:-birth_year, -nkids), ~ifelse(. < 0, NA, .)) %>%
  mutate_at(vars(-scram:-birth_year, -nkids, -rhispanic, -rrace, -starts_with("foodsufr"), -starts_with("wherefree")), as.factor) %>%
  mutate_at(vars(starts_with("foodsufr"), starts_with("wherefree")), as.logical) %>%
  mutate(race = ifelse(rhispanic == 2, "latino", rrace) %>%
           as.factor() %>%
           fct_recode(white = "1", black = "2", asian = "3", other = "4") %>%
           fct_relevel("white", "black", "latino"),
         gender = fct_recode(gender, male = "1", female = "2"),
         wrkloss = fct_recode(wrkloss, loss = "1", no_loss = "2"),
         delay_care = fct_recode(delay_care, delayed = "1", no_delay = "2"),
         miss_care = fct_recode(miss_care, missed = "1", no_miss = "2"),
         anxious = fct_collapse(anxious, not_anxious = c("1", "2"), most_all_days = c("3", "4")),
         tenure = fct_recode(tenure, own_in_full = "1", mortgage = "2", rent = "3", other = "4"),
         last_housing = fct_recode(last_housing, on_time = "1", late = "2", deferred = "3"),
         housing_conf = fct_collapse(housing_conf, not_confident = c("1", "2"), confident = c("3", "4"), deferred = "5"),
         internet = fct_collapse(internet, always_usually = c("1", "2"), not_reliable = c("3", "4", "5")),
         hh_income = fct_collapse(hh_income, under35k = c("1", "2"), income35k_75k = c("3", "4"), income75k_150k = c("5", "6"), income150k_plus = c("7", "8")),
         age = 2020 - birth_year,
         kids_present = as.factor(ifelse(nkids > 0, "kids_in_house", "no_kids")),
         freefood = fct_recode(freefood, received_food = "1", no_free_food = "2"),
         age_range = cut(age, breaks = c(18, 34, 64, Inf), labels = c("ages18_34", "ages35_64", "ages65plus"), include.lowest = TRUE),
         wks_incl = paste(range(as.numeric(week)), collapse = "_")
  ) %>%
  mutate_at(vars(prior_food, current_food), fct_collapse, secure = "1", not_kinds_wanted = "2", insecure = c("3", "4")) %>%
  left_join(week_dates, by = "week") %>%
  mutate(week = as.factor(week)) %>%
  select(state, wks_incl, week, start_date, end_date, everything(), -rhispanic, -rrace, -birth_year)

summary(pums_df)
```

```{r}
us_srvy <- as_survey_design(pums_df, weights = pweight, strata = week)
ct_srvy <- as_survey_design(pums_df %>% filter(state == "09"), weights = pweight, strata = week)
srvys <- lst(us_srvy, ct_srvy) %>% 
  set_names(substr, 1, 2) %>%
  # assume grouped for all weeks
  map(group_by, wks_incl)

trends <- list()
by_group <- list()
```

# trends

in general, there aren't really any changes over time. so at least things aren't getting *worse*, but don't seem to be letting up either. interesting since some of the questions are cumulative, e.g. work loss is any loss since 3/13, so you'd imagine that number would continue to grow, but it hasn't so far. suggests that by the time the first week of the survey was done (4/23), that damage had already been done.

## lost work

no change

```{r}
trends$work_loss <- srvys %>%
  map(filter, !is.na(wrkloss)) %>%
  compare_share(week, wrkloss) %>%
  filter(wrkloss == "loss") 

trends$work_loss
```

## food insecurity (current)

not much of any change

```{r}
trends$food_insecurity <- srvys %>%
  map(filter, !is.na(current_food)) %>%
  compare_share(week, current_food) %>%
  filter(current_food == "insecure")

trends$food_insecurity
```




## delayed medical care

US is steady, but CT was trending up

```{r}
trends$delayed_med_care <- srvys %>%
  map(filter, !is.na(delay_care)) %>%
  compare_share(week, delay_care) %>%
  filter(delay_care == "delayed")

trends$delayed_med_care %>%
  mutate(week = as.numeric(week)) %>%
  ggplot(aes(x = week, y = share, color = name)) +
  geom_line(size = 0.8) +
  geom_point() +
  scale_color_carto_d(palette = "Vivid") +
  # scale_x_continuous(breaks = 1:6) +
  labs(title = "delayed medical care")
```

## missed care

~~not changing~~ or fluctuating

```{r}
trends$missed_med_care <- srvys %>%
  map(filter, !is.na(miss_care)) %>%
  compare_share(week, miss_care) %>%
  filter(miss_care == "missed")

trends$missed_med_care
```

## anxiety

steady/fluctuating

```{r}
trends$anxiety <- srvys %>%
  map(filter, !is.na(anxious)) %>%
  compare_share(week, anxious) %>%
  filter(anxious == "most_all_days")

trends$anxiety
```



## housing insecure—can't pay next month

~~not changing~~ fluctuating

```{r}
trends$housing_insecurity <- srvys %>%
  map(filter, !is.na(housing_conf)) %>%
  compare_share(week, housing_conf) %>%
  filter(housing_conf == "not_confident")

trends$housing_insecurity
```

## food insecurity: current vs prior

pretty interesting: only 2 percent of people that were secure before pandemic are insecure currently, but 20 percent no longer have food they *want*. Vast majority stay in whatever condition they were already in. Not too many dropped from secure to insecure, and 16 percent of insecure moved up to not having kinds of food wanted—maybe due to amount of food giveaways now happening?

```{r}
trends$food_insecurity_change <- srvys %>%
  map(filter, !is.na(current_food), !is.na(prior_food)) %>%
  compare_share(prior_food, current_food)

trends$food_insecurity_change
```



```{r}
food_change <- ct_srvy %>%
  filter(!is.na(prior_food), !is.na(current_food)) %>%
  mutate(id = interaction(prior_food, current_food, sep = ",")) %>%
  group_by(id) %>%
  summarise(share = survey_mean()) %>%
  separate(id, into = c("prior_food", "current_food"), sep = ",", remove = FALSE) %>%
  arrange(desc(prior_food)) %>%
  mutate_at(vars(prior_food, current_food), as_factor) %>%
  mutate(id = fct_inorder(id)) %>%
  pivot_longer(ends_with("food"), names_to = "point", names_ptypes = list(point = factor())) %>%
  mutate(p = str_extract(id, "^\\w+"))

ggplot(food_change, aes(y = share, x = fct_rev(point), stratum = value, alluvium = id)) +
  geom_alluvium(aes(fill = id), alpha = 0.85, width = 0.1) +
  geom_stratum(width = 0.1) +
  geom_text(stat = "stratum", infer.label = TRUE, size = 2.8) +
  scale_fill_manual(values = c(carto_pal(3, "RedOr"), carto_pal(3, "Purp"), carto_pal(3, "Teal"))) +
  scale_x_discrete(expand = expansion(mult = 0)) +
  coord_flip()  +
  theme_minimal() +
  theme(legend.position = "none") 
```


Flipped around: of the people currently food insecure, what was their condition before pandemic? CT data is pretty messy. Could be a trend in past couple weeks of people who were secure before covid now becoming insecure recently, or could be fluke

```{r}
trends$became_food_insecure <- srvys %>%
  map(filter, !is.na(current_food), !is.na(prior_food)) %>%
  compare_share(week, current_food, prior_food) %>%
  filter(current_food == "insecure")

trends$became_food_insecure %>%
  filter(name == "US") %>%
  ggplot(aes(x = as.numeric(week), y = share, fill = prior_food, color = prior_food)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  scale_color_manual(values = carto_pal(7, "Vivid"))
```


# by group



## work loss

```{r message=TRUE, warning=TRUE}
by_group$work_loss <- srvys %>%
  compare_grps(wrkloss) %>%
  map(filter, wrkloss == "loss") %>%
  combine_dimensions(c(wks_incl, wrkloss))
```

## food insecurity (current)

```{r}
by_group$food_insecurity <- srvys %>%
  compare_grps(current_food) %>%
  map(filter, current_food == "insecure") %>%
  combine_dimensions(c(wks_incl, current_food))
```

change less in share not having enough food, but share having limited options

```{r}
by_group$food_insecurity_change <- list(
  srvys %>%
    map(filter, !is.na(prior_food), !is.na(current_food)) %>%
    compare_share(kids_present, prior_food) %>%
    filter(prior_food != "secure"),
  srvys %>%
    map(filter, !is.na(prior_food), !is.na(current_food)) %>%
    compare_share(kids_present, current_food) %>%
    filter(current_food != "secure")
) %>%
  map(select, -share_se) %>%
  map_dfr(pivot_longer, ends_with("_food"), names_to = "variable", values_to = "group", names_ptypes = list(variable = factor()))

by_group$food_insecurity_change %>%
  ggplot(aes(x = variable, y = share, fill = group)) +
  geom_col(position = position_stack(), width = 0.8) +
  scale_fill_carto_d(palette = "Vivid") +
  facet_wrap(vars(name, kids_present)) +
  labs(title = "previous vs current food insecurity")
```

## received free food

```{r}
by_group$free_food <- srvys %>%
  compare_grps(freefood) %>%
  map(filter, freefood == "received_food") %>%
  combine_dimensions(c(wks_incl, freefood))
```


## delayed care

```{r}
by_group$delayed_med_care <- srvys %>%
  compare_grps(delay_care) %>%
  map(filter, delay_care == "delayed") %>%
  combine_dimensions(c(wks_incl, delay_care))
```

## missed care

```{r}
by_group$missed_med_care <- srvys %>%
  compare_grps(miss_care) %>%
  map(filter, miss_care == "missed") %>%
  combine_dimensions(c(wks_incl, miss_care))
```

## anxiety

```{r}
by_group$anxiety <- srvys %>%
  compare_grps(anxious) %>%
  map(filter, anxious == "most_all_days") %>%
  combine_dimensions(c(wks_incl, anxious))
```


## housing insecurity—next month

```{r}
by_group$housing_insecurity <- srvys %>%
  compare_grps(housing_conf) %>%
  map(filter, housing_conf == "not_confident") %>%
  combine_dimensions(c(wks_incl, housing_conf))
```

### renters only

```{r}
by_group$renter_insecurity <- srvys %>%
  map(filter, tenure == "rent") %>%
  compare_grps(housing_conf) %>%
  map(filter, housing_conf == "not_confident") %>%
  combine_dimensions(c(wks_incl, housing_conf))
```

## internet reliably available for kids' education

kinda messy & large MOEs, not keeping

```{r}
# messy
internet_no_output <- srvys %>%
  compare_grps(internet, age_range = FALSE, kids_present = FALSE) %>%
  map(filter, internet == "not_reliable") %>%
  combine_dimensions(c(wks_incl, internet))
```

```{r}
compare_bars <- function(df) {
  ggplot(df, aes(x = fct_rev(group), y = share, fill = dimension)) +
  geom_col(width = 0.8) +
  coord_flip() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), labels = scales::percent_format(accuracy = 1)) +
  scale_fill_carto_d(palette = "Vivid") +
  facet_grid(rows = vars(dimension), scales = "free_y", space = "free") +
  theme_minimal() +
  theme(legend.position = "none",
        axis.ticks = element_blank(),
        plot.title.position = "plot") +
    labs(subtitle = "CT groups, all weeks", x = NULL, y = NULL)
}
```


```{r}
by_group <- by_group %>% map(filter, group != "other")

by_group$work_loss %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(x = NULL, y = NULL,
       title = "loss of employment income since 3/13")

by_group$food_insecurity %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(x = NULL, y = NULL,
       title = "food insecurity in past 7 days")

by_group$delayed_med_care  %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(x = NULL, y = NULL,
       title = "delayed medical care in past 4 weeks")

by_group$missed_med_care  %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(x = NULL, y = NULL,
       title = "missed medical care not related to covid in past 4 weeks")

by_group$anxiety %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(x = NULL, y = NULL,
       title = "anxiety half the days in past week or more")

by_group$housing_insecurity %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(x = NULL, y = NULL,
       title = "little/no confidence in making next housing payment")

by_group$renter_insecurity %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(x = NULL, y = NULL,
       title = "little/no confidence in making next housing payment--renters only")
```



```{r}
saveRDS(trends, here::here("output_data/hhp_trends.rds"))
saveRDS(by_group, here::here("output_data/hhp_by_group.rds"))
```

# specific food access questions

food sufficiency questions universe: current food not enough / not types wanted

```{r}
# just a little easier to handle food vars separately
food_df <- pums_df %>%
  select(state:hh_income, race, age_range, kids_present, current_food, cant_afford = foodsufrsn1, transportation = foodsufrsn2, afraid_to_go_out = foodsufrsn3, need_delivered = foodsufrsn4, stores_didnt_have_food = foodsufrsn5, freefood, school = wherefree1, pantry = wherefree2, home_delivery = wherefree3, church = wherefree4, shelter = wherefree5, comm_program = wherefree6, family = wherefree7) %>%
  mutate_at(vars(cant_afford:stores_didnt_have_food), ~case_when(
    current_food == "secure" ~ NA_character_,
    is.na(.) ~ "didnt_need",
    TRUE ~ "needed"
  ) %>% as.factor()) %>%
  mutate_at(vars(school:family), ~case_when(
    freefood == "no_free_food" ~ NA_character_,
    is.na(.) ~ "didnt_use_source",
    TRUE ~ "used_source"
  ) %>% as.factor())

summary(food_df)

fsrvys <- list(
  us = as_survey_design(food_df, weights = pweight),
  ct = as_survey_design(food_df %>% filter(state == "09"), weights = pweight)
) %>%
  map(group_by, wks_incl)

```

## sources of free food

of adults getting free food in past 7 days

```{r}
food_sources <- food_df %>%
  select(school:family) %>%
  names() %>%
  set_names() %>%
  map(function(col_name) {
    col <- sym(col_name)
    fsrvys %>%
      compare_grps({{ col }}, hh_income = FALSE) %>%
      map(filter, {{ col }} == "used_source") %>%
      combine_dimensions(c(wks_incl, {{ col }}))
  }) %>%
  map(filter, group != "other")
```





```{r}
food_sources$school %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(title = "received free food through schools, other kids' programs",
       caption = "of adults receiving free food in past 7 days")
```

```{r}
food_sources$family %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(title = "received free food through family or friends",
       caption = "of adults receiving free food in past 7 days")
```

```{r}
food_sources$pantry %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(title = "received free food through food pantry / food bank",
       caption = "of adults receiving free food in past 7 days")
```

Key takeaway: people living with kids rely heavily on schools for food, whereas people not living with kids & seniors rely heavily on food pantries & food banks.

```{r}
food_sources %>%
  map_dfr(pivot_longer, -c(name, wks_incl, share:group), names_to = "source") %>%
  filter(name == "CT", dimension == "total") %>%
  mutate(source = as_factor(source) %>% fct_reorder(share, .fun = max)) %>%
  ggplot(aes(x = source, y = share)) +
  geom_col(width = 0.8, fill = "#008b60") +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), color = "white", hjust = 1, nudge_y = -2e-3, size = 2.5, fontface = "bold") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), breaks = NULL) +
  coord_flip() +
  theme_minimal() +
  theme(panel.grid = element_blank(),
        axis.ticks = element_blank(),
        plot.title.position = "plot") +
  labs(title = "source of free food",
       x = NULL, y = NULL)
```


## barriers to food access

of adults experiencing shortage of food / desired types of food in past 7 days

```{r}
food_barriers <- food_df %>%
  select(cant_afford:stores_didnt_have_food) %>%
  names() %>%
  set_names() %>%
  map(function(col_name) {
    col <- sym(col_name)
    fsrvys %>%
      compare_grps({{ col }}, hh_income = FALSE) %>%
      map(filter, {{ col }} == "needed") %>%
      combine_dimensions(c(wks_incl, {{ col }}))
  }) %>%
  map(filter, group != "other")
```



```{r}
food_barriers$cant_afford %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(title = "couldn't afford food",
       caption = "of adults not having enough / desired food in past 7 days")
```

```{r}
food_barriers$transportation %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(title = "needed transportation to get food",
       caption = "of adults not having enough / desired food in past 7 days")
```

```{r}
food_barriers$need_delivered %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(title = "needed food delivered",
       caption = "of adults not having enough / desired food in past 7 days")
```

## resources x health

Interested in how anxiety differs by food insecurity, housing insecurity, etc

```{r}
resource_x_health <- list()
```

```{r fig.height=6}
resource_x_health$anxiety_x_food <- srvys %>%
  map(filter, !is.na(current_food), !is.na(anxious)) %>%
  compare_share(current_food, anxious) %>%
  filter(anxious == "most_all_days", name == "CT")

resource_x_health$anxiety_x_housing <- srvys %>%
  map(filter, !is.na(housing_conf), !is.na(anxious)) %>%
  compare_share(housing_conf, anxious) %>%
  filter(anxious == "most_all_days", name == "CT")

resource_x_health$anxiety_x_delay_care <- srvys %>%
  map(filter, !is.na(delay_care), !is.na(anxious)) %>%
  compare_share(delay_care, anxious) %>%
  filter(anxious == "most_all_days", name == "CT")

resource_x_health$anxiety_x_tenure <- srvys %>%
  map(filter, !is.na(tenure), !is.na(anxious)) %>%
  compare_share(tenure, anxious) %>%
  filter(anxious == "most_all_days", name == "CT", tenure != "other")

resource_x_health %>%
  map_dfr(pivot_longer, c(-name, -wks_incl, -anxious, -starts_with("share")), names_to = "measure", values_to = "group") %>%
  mutate_at(vars(measure, group), fct_relabel, camiller::clean_titles) %>%
  mutate(measure = fct_recode(measure, "Food insecure" = "Current food", "Confidence in next housing payment" = "Housing conf")) %>%
  ggplot(aes(x = group, y = share)) +
  geom_col(width = 0.8, fill = "#008b60") +
  geom_text(aes(label = scales::percent(share, accuracy = 1)), size = 2.8, hjust = 1, nudge_y = -8e-3, fontface = "bold", color = "white") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), breaks = NULL) +
  facet_grid(rows = vars(measure), scales = "free", space = "free", switch = "y",
             labeller = labeller(measure = label_wrap_gen(20))) +
  coord_flip() +
  labs(x = NULL, y = NULL,
       title = "Anxiety rate vs access to resources") +
  theme(strip.text.y = element_text(angle = 0, face = "bold"),
        strip.placement = "outside",
        panel.grid = element_blank(),
        plot.title.position = "plot",
        panel.spacing = unit(0.2, "in"))
```

Not super surprising: people are more anxious who have also been food insecure, delayed medical care, worried about next housing payment, and who rent. Definitely more we could dig into here.


```{r}
saveRDS(food_sources, here::here("output_data/hhp_sources_of_food.rds"))
saveRDS(food_barriers, here::here("output_data/hhp_barriers_to_food.rds"))
```

```{r}
write_csv(week_dates, here::here("_utils/pums_week_dates.csv"))
```


Not ready yet: curious about how many people have become food insecure / experienced insecurity at some point

```{r message=TRUE, warning=TRUE}
rep_ids <- all_pums %>%
  map_dfr(janitor::clean_names, .id = "wk") %>%
  filter(est_st == "09", !is.na(curfoodsuf)) %>%
  count(scram) %>%
  arrange(-n) %>%
  filter(n > 1)

ct_srvy %>%
  filter(!is.na(current_food)) %>%
  # as_tibble() %>%
  group_by(scram) %>%
  mutate(insecure = current_food == "insecure",
         insecure_so_far = cumsum(insecure) > 0) %>%
  ungroup() %>%
  select(scram, week, current_food, insecure, insecure_so_far) %>%
  # arrange(scram)
  group_by(week) %>%
  summarise(share_current = survey_mean(insecure, na.rm = TRUE),
            share_ever = survey_mean(insecure_so_far, na.rm = TRUE, vartype = "ci", level = 0.9))
```


