---
title: "pums analysis, multi weeks"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = TRUE
)
```

```{r}
library(tidyverse)
library(srvyr)
library(rvest)
library(rcartocolor)
```

```{r}
survey_share_by <- function(srvy, ..., digits = 2, vartype = "se") {
  grp_vars <- quos(...)
  srvy %>%
    group_by(!!!grp_vars) %>%
    summarise(share = survey_mean(vartype = vartype, level = 0.9)) %>%
    mutate_at(vars(matches("share")), round, digits = digits)
}

compare_share <- function(srvy_lst, ...) {
  srvy_lst %>%
    map_dfr(survey_share_by, ..., .id = "name") %>%
    mutate(name = as_factor(name) %>% fct_relabel(toupper))
}

combine_dimensions <- function(dfs, drop_col) {
  dfs %>%
    map(select, -{{ drop_col }}, -share_se) %>%
    map_dfr(pivot_longer, -c(name, share), names_to = "dimension", values_to = "group",
            names_ptypes = list(dimension = factor())) %>%
    mutate(group = as_factor(ifelse(group == "total", as.character(name), as.character(group))))
}
```

```{r}
week_dates <- read_html("https://www.census.gov/programs-surveys/household-pulse-survey/datasets.html") %>%
  html_nodes("h4.uscb-h4") %>%
  html_text() %>%
  str_match_all("([A-Z][a-z]+ \\d{1,2})") %>%
  map(~.[, 1]) %>%
  rev() %>%
  map(paste, "2020") %>%
  map(lubridate::mdy) %>%
  map(enframe, name = "pt", value = "date") %>%
  map_dfr(mutate, pt = fct_recode(as.character(pt), start = "1", end = "2"), .id = "week") %>%
  pivot_wider(names_from = pt, names_glue = "{pt}_{.value}", values_from = date) %>%
  mutate(week = as.numeric(week))
```


```{r}
all_pums <- list.files(here::here("fetch_data/microdata"), full.names = TRUE) %>%
  map(readRDS)

pums_df <- all_pums %>% 
  map(janitor::clean_names) %>%
  map_dfr(select, state = est_st, week, pweight, birth_year = tbirth_year, gender = egender, rhispanic, rrace, hh_income = income, nkids = thhld_numkid, wrkloss, prior_food = prifoodsuf, current_food = curfoodsuf, delay_care = delay, miss_care = notget, tenure, last_housing = mortlmth, housing_conf = mortconf, internet = intrntavail, starts_with("foodsufr"), freefood, starts_with("wherefree")) %>%
  mutate_at(vars(-state:-birth_year, -nkids), ~ifelse(. < 0, NA, .)) %>%
  mutate_at(vars(-state:-birth_year, -nkids, -rhispanic, -rrace, -starts_with("foodsufr"), -starts_with("wherefree")), as.factor) %>%
  mutate_at(vars(starts_with("foodsufr"), starts_with("wherefree")), as.logical) %>%
  mutate(race = ifelse(rhispanic == 2, "latino", rrace) %>%
           as.factor() %>%
           fct_recode(white = "1", black = "2", asian = "3", other = "4") %>%
           fct_relevel("white", "black", "latino"),
         gender = fct_recode(gender, male = "1", female = "2"),
         wrkloss = fct_recode(wrkloss, loss = "1", no_loss = "2"),
         delay_care = fct_recode(delay_care, delayed = "1", no_delay = "2"),
         miss_care = fct_recode(miss_care, missed = "1", no_miss = "2"),
         tenure = fct_recode(tenure, own_in_full = "1", mortgage = "2", rent = "3", other = "4"),
         last_housing = fct_recode(last_housing, on_time = "1", late = "2", deferred = "3"),
         housing_conf = fct_collapse(housing_conf, not_confident = c("1", "2"), confident = c("3", "4"), deferred = "5"),
         internet = fct_collapse(internet, always_usually = c("1", "2"), not_reliable = c("3", "4", "5")),
         hh_income = fct_collapse(hh_income, under35 = c("1", "2"), income35_75 = c("3", "4"), income75_150 = c("5", "6"), income150_plus = c("7", "8")),
         age = 2020 - birth_year,
         kids_present = as.factor(ifelse(nkids > 0, "kids_in_house", "no_kids")),
         freefood = fct_recode(freefood, received_food = "1", no_free_food = "2"),
         age_range = cut(age, breaks = c(18, 34, 64, Inf), labels = c("ages18_34", "ages35_64", "ages65plus"), include.lowest = TRUE)
  ) %>%
  mutate_at(vars(prior_food, current_food), fct_collapse, secure = "1", not_kinds_wanted = "2", insecure = c("3", "4")) %>%
  left_join(week_dates, by = "week") %>%
  mutate(week = as.factor(week)) %>%
  select(state, week, start_date, end_date, everything(), -rhispanic, -rrace, -birth_year)

summary(pums_df)
```

```{r}
us_srvy <- as_survey_design(pums_df, weights = pweight)
ct_srvy <- as_survey_design(pums_df %>% filter(state == "09"), weights = pweight)
srvys <- lst(us_srvy, ct_srvy) %>% set_names(substr, 1, 2)

trends <- list()
by_group <- list()
```

# trends

in general, there aren't really any changes over time. so at least things aren't getting *worse*, but don't seem to be letting up either. interesting since some of the questions are cumulative, e.g. work loss is any loss since 3/13, so you'd imagine that number would continue to grow, but it hasn't so far. suggests that by the time the first week of the survey was done (4/23), that damage had already been done.

## lost work

no change

```{r}
trends$work_loss <- srvys %>%
  map(filter, !is.na(wrkloss)) %>%
  compare_share(week, wrkloss) %>%
  filter(wrkloss == "loss") 

trends$work_loss
```

## food insecurity (current)

not much of any change

```{r}
trends$food_insecurity <- srvys %>%
  map(filter, !is.na(current_food)) %>%
  compare_share(week, current_food) %>%
  filter(current_food == "insecure")
```

## delayed medical care

US is steady, but CT trending up

```{r}
trends$delayed_med_care <- srvys %>%
  map(filter, !is.na(delay_care)) %>%
  compare_share(week, delay_care) %>%
  filter(delay_care == "delayed")

trends$delayed_med_care %>%
  mutate(week = as.numeric(week)) %>%
  ggplot(aes(x = week, y = share, color = name)) +
  geom_line(size = 0.8) +
  geom_point() +
  scale_color_carto_d(palette = "Vivid") +
  scale_x_continuous(breaks = 1:6) +
  labs(title = "delayed medical care")
```

## missed care

not changing

```{r}
trends$missed_med_care <- srvys %>%
  map(filter, !is.na(miss_care)) %>%
  compare_share(week, miss_care) %>%
  filter(miss_care == "missed")
```

## housing insecure—can't pay next month

not changing

```{r}
trends$housing_insecurity <- srvys %>%
  map(filter, !is.na(housing_conf)) %>%
  compare_share(week, housing_conf) %>%
  filter(housing_conf == "not_confident")
```




# by group

## work loss

```{r}
work_loss <- list()

work_loss$total <- srvys %>%
  map(filter, !is.na(wrkloss)) %>%
  compare_share(total = "total", wrkloss)

work_loss$by_age <- srvys %>%
  map(filter, !is.na(wrkloss)) %>%
  compare_share(age_range, wrkloss)

work_loss$by_race <- srvys %>%
  map(filter, !is.na(wrkloss), race != "other") %>%
  compare_share(race, wrkloss)

work_loss$by_income <- srvys %>%
  map(filter, !is.na(wrkloss), !is.na(hh_income)) %>%
  compare_share(hh_income, wrkloss)

work_loss$by_kids <- srvys %>%
  map(filter, !is.na(wrkloss)) %>%
  compare_share(kids_present, wrkloss)

by_group$work_loss <- work_loss %>%
  map(filter, wrkloss == "loss") %>%
  combine_dimensions(wrkloss)
```




## food insecurity (current)

```{r}
food_insecurity <- list()

food_insecurity$total <- srvys %>%
  map(filter, !is.na(current_food)) %>%
  compare_share(total = "total", current_food)

food_insecurity$by_age <- srvys %>%
  map(filter, !is.na(current_food)) %>%
  compare_share(age_range, current_food)

food_insecurity$by_race <- srvys %>%
  map(filter, !is.na(current_food), race != "other") %>%
  compare_share(race, current_food)

food_insecurity$by_income <- srvys %>%
  map(filter, !is.na(current_food), !is.na(hh_income)) %>%
  compare_share(hh_income, current_food)

food_insecurity$by_kids <- srvys %>%
  map(filter, !is.na(current_food)) %>%
  compare_share(kids_present, current_food)

by_group$food_insecurity <- food_insecurity %>%
  map(filter, current_food == "insecure") %>%
  combine_dimensions(current_food)
```

change less in share not having enough food, but share having limited options

```{r}
by_group$food_insecurity_change <- list(
  srvys %>%
    map(filter, !is.na(prior_food), !is.na(current_food)) %>%
    compare_share(kids_present, prior_food) %>%
    filter(prior_food != "secure"),
  srvys %>%
    map(filter, !is.na(prior_food), !is.na(current_food)) %>%
    compare_share(kids_present, current_food) %>%
    filter(current_food != "secure")
) %>%
  map(select, -share_se) %>%
  map_dfr(pivot_longer, ends_with("_food"), names_to = "variable", values_to = "group", names_ptypes = list(variable = factor()))

by_group$food_insecurity_change %>%
  ggplot(aes(x = variable, y = share, fill = group)) +
  geom_col(position = position_stack(), width = 0.8) +
  scale_fill_carto_d(palette = "Vivid") +
  facet_wrap(vars(name, kids_present)) +
  labs(title = "previous vs current food insecurity")
```

## delayed care

```{r}
delayed_med_care <- list()

delayed_med_care$total <- srvys %>%
  map(filter, !is.na(delay_care)) %>%
  compare_share(total = "total", delay_care)

delayed_med_care$by_age <- srvys %>%
  map(filter, !is.na(delay_care)) %>%
  compare_share(age_range, delay_care)

delayed_med_care$by_race <- srvys %>%
  map(filter, !is.na(delay_care), race != "other") %>%
  compare_share(race, delay_care)

delayed_med_care$by_income <- srvys %>%
  map(filter, !is.na(delay_care), !is.na(hh_income)) %>%
  compare_share(hh_income, delay_care)

delayed_med_care$by_kids <- srvys %>%
  map(filter, !is.na(delay_care)) %>%
  compare_share(kids_present, delay_care)

by_group$delayed_med_care <- delayed_med_care %>%
  map(filter, delay_care == "delayed") %>%
  combine_dimensions(delay_care)
```

## missed care

```{r}
missed_med_care <- list()

missed_med_care$total <- srvys %>%
  map(filter, !is.na(miss_care)) %>%
  compare_share(total = "total", miss_care)

missed_med_care$by_age <- srvys %>%
  map(filter, !is.na(miss_care)) %>%
  compare_share(age_range, miss_care)

missed_med_care$by_race <- srvys %>%
  map(filter, !is.na(miss_care), race != "other") %>%
  compare_share(race, miss_care)

missed_med_care$by_income <- srvys %>%
  map(filter, !is.na(miss_care), !is.na(hh_income)) %>%
  compare_share(hh_income, miss_care)

missed_med_care$by_kids <- srvys %>%
  map(filter, !is.na(miss_care)) %>%
  compare_share(kids_present, miss_care)

by_group$missed_med_care <- missed_med_care %>%
  map(filter, miss_care == "missed") %>%
  combine_dimensions(miss_care)
```


## housing insecurity—next month

```{r}
housing_insecurity <- list()

housing_insecurity$total <- srvys %>%
  map(filter, !is.na(housing_conf)) %>%
  compare_share(total = "total", housing_conf)

housing_insecurity$by_age <- srvys %>%
  map(filter, !is.na(housing_conf)) %>%
  compare_share(age_range, housing_conf)

housing_insecurity$by_race <- srvys %>%
  map(filter, !is.na(housing_conf), race != "other") %>%
  compare_share(race, housing_conf)

housing_insecurity$by_income <- srvys %>%
  map(filter, !is.na(housing_conf), !is.na(hh_income)) %>%
  compare_share(hh_income, housing_conf) 

housing_insecurity$by_kids <- srvys %>%
  map(filter, !is.na(housing_conf)) %>%
  compare_share(kids_present, housing_conf) 

by_group$housing_insecurity <- housing_insecurity %>%
  map(filter, housing_conf == "not_confident") %>%
  combine_dimensions(housing_conf)

```

### renters only

```{r}
renter_insecurity <- list()

renter_insecurity$total <- srvys %>%
  map(filter, !is.na(housing_conf), tenure == "rent") %>%
  compare_share(total = "total", housing_conf)

renter_insecurity$by_age <- srvys %>%
  map(filter, !is.na(housing_conf), tenure == "rent") %>%
  compare_share(age_range, housing_conf)

renter_insecurity$by_race <- srvys %>%
  map(filter, !is.na(housing_conf), race != "other", tenure == "rent") %>%
  compare_share(race, housing_conf)

renter_insecurity$by_income <- srvys %>%
  map(filter, !is.na(housing_conf), !is.na(hh_income), tenure == "rent") %>%
  compare_share(hh_income, housing_conf) 

renter_insecurity$by_kids <- srvys %>%
  map(filter, !is.na(housing_conf), tenure == "rent") %>%
  compare_share(kids_present, housing_conf)

by_group$renter_insecurity <- renter_insecurity %>%
  map(filter, housing_conf == "not_confident") %>%
  combine_dimensions(housing_conf)
```

## internet reliably available for kids' education

kinda messy & large MOEs, not keeping

```{r}
internet_kids <- list()

internet_kids$total <- srvys %>%
  map(filter, !is.na(internet)) %>%
  compare_share(total = "total", internet)

internet_kids$by_race <- srvys %>%
  map(filter, !is.na(internet), race != "other") %>%
  compare_share(race, internet)

internet_kids$by_income <- srvys %>%
  map(filter, !is.na(internet), !is.na(hh_income)) %>%
  compare_share(hh_income, internet) 


# messy
internet_kids <- internet_kids %>%
  map(filter, internet == "not_reliable") %>%
  combine_dimensions(internet)

```

```{r}
compare_bars <- function(df) {
  ggplot(df, aes(x = fct_rev(group), y = share, fill = dimension)) +
  geom_col(width = 0.8) +
  coord_flip() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), labels = scales::percent_format(accuracy = 1)) +
  scale_fill_carto_d(palette = "Vivid") +
  facet_grid(rows = vars(dimension), scales = "free_y", space = "free") +
  theme_minimal() +
  theme(legend.position = "none",
        axis.ticks = element_blank(),
        plot.title.position = "plot") +
    labs(subtitle = "CT groups, all weeks", x = NULL, y = NULL)
}
```


```{r}
by_group$work_loss %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(x = NULL, y = NULL,
       title = "loss of employment income since 3/13")

by_group$food_insecurity %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(x = NULL, y = NULL,
       title = "food insecurity in past 7 days")

by_group$delayed_med_care  %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(x = NULL, y = NULL,
       title = "delayed medical care in past 4 weeks")

by_group$missed_med_care  %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(x = NULL, y = NULL,
       title = "missed medical care not related to covid in past 4 weeks")

by_group$housing_insecurity %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(x = NULL, y = NULL,
       title = "little/no confidence in making next housing payment")

by_group$renter_insecurity %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(x = NULL, y = NULL,
       title = "little/no confidence in making next housing payment--renters only")
```



```{r}
saveRDS(trends, here::here("output_data/hhp_trends.rds"))
saveRDS(by_group, here::here("output_data/hhp_by_group.rds"))
```

# specific food access questions

food sufficiency questions universe: current food not enough / not types wanted

```{r}
# just a little easier to label food vars separately
food_df <- pums_df %>%
  select(state:hh_income, race, age_range, kids_present, current_food, cant_afford = foodsufrsn1, transportation = foodsufrsn2, need_delivered = foodsufrsn4, freefood, school = wherefree1, pantry = wherefree2, home_delivery = wherefree3, church = wherefree4, shelter = wherefree5, comm_program = wherefree6, family = wherefree7) %>%
  mutate_at(vars(cant_afford:need_delivered), ~case_when(
    current_food == "secure" ~ NA_character_,
    is.na(.) ~ "didnt_need",
    TRUE ~ "needed"
  ) %>% as.factor()) %>%
  mutate_at(vars(school:family), ~case_when(
    freefood == "no_free_food" ~ NA_character_,
    is.na(.) ~ "didnt_use_source",
    TRUE ~ "used_source"
  ) %>% as.factor())

summary(food_df)

fsrvys <- list(
  us = as_survey_design(food_df, weights = pweight),
  ct = as_survey_design(food_df %>% filter(state == "09"), weights = pweight)
)

```

## sources of free food

of adults getting free food in past 7 days

```{r}
food_sources <- list()
```

```{r}
# these should be functions
school <- list()
school$total <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(school)) %>%
  compare_share(total = "total", school)

school$by_gender <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(school)) %>%
  compare_share(gender, school)

school$by_race <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(school), race != "other") %>%
  compare_share(race, school)

school$by_age <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(school)) %>%
  compare_share(age_range, school)

school$kids_present <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(school)) %>%
  compare_share(kids_present, school)

food_sources$school <- school %>%
  map(filter, school == "used_source") %>%
  combine_dimensions(school)
```

```{r}
pantry <- list()
pantry$total <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(pantry)) %>%
  compare_share(total = "total", pantry)

pantry$by_gender <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(pantry)) %>%
  compare_share(gender, pantry)

pantry$by_race <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(pantry), race != "other") %>%
  compare_share(race, pantry)

pantry$by_age <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(pantry)) %>%
  compare_share(age_range, pantry)

pantry$kids_present <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(pantry)) %>%
  compare_share(kids_present, pantry)

food_sources$pantry <- pantry %>%
  map(filter, pantry == "used_source") %>%
  combine_dimensions(pantry)
```

```{r}
family <- list()
family$total <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(family)) %>%
  compare_share(total = "total", family)

family$by_gender <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(family)) %>%
  compare_share(gender, family)

family$by_race <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(family), race != "other") %>%
  compare_share(race, family)

family$by_age <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(family)) %>%
  compare_share(age_range, family)

family$kids_present <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(family)) %>%
  compare_share(kids_present, family)

food_sources$family <- family %>%
  map(filter, family == "used_source") %>%
  combine_dimensions(family)
```

```{r}
food_sources$school %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(title = "received free food through schools, other kids' programs",
       caption = "of adults receiving free food in past 7 days")
```

```{r}
food_sources$family %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(title = "received free food through family or friends",
       caption = "of adults receiving free food in past 7 days")
```

```{r}
food_sources$pantry %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(title = "received free food through food pantry / food bank",
       caption = "of adults receiving free food in past 7 days")
```

Key takeaway: people living with kids rely heavily on schools for food, whereas people not living with kids & seniors rely heavily on food pantries & food banks.

## barriers to food access

of adults experiencing shortage of food / desired types of food in past 7 days

```{r}
food_barriers <- list()
```

```{r}
cant_afford <- list()
cant_afford$total <- fsrvys %>%
  map(filter, !is.na(current_food), !is.na(cant_afford)) %>%
  compare_share(total = "total", cant_afford)

cant_afford$by_gender <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(cant_afford)) %>%
  compare_share(gender, cant_afford)

cant_afford$by_race <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(cant_afford), race != "other") %>%
  compare_share(race, cant_afford)

cant_afford$by_age <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(cant_afford)) %>%
  compare_share(age_range, cant_afford)

cant_afford$kids_present <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(cant_afford)) %>%
  compare_share(kids_present, cant_afford)

food_barriers$cant_afford <- cant_afford %>%
  map(filter, cant_afford == "needed") %>%
  combine_dimensions(cant_afford)
```

```{r}
transportation <- list()
transportation$total <- fsrvys %>%
  map(filter, !is.na(current_food), !is.na(transportation)) %>%
  compare_share(total = "total", transportation)

transportation$by_gender <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(transportation)) %>%
  compare_share(gender, transportation)

transportation$by_race <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(transportation), race != "other") %>%
  compare_share(race, transportation)

transportation$by_age <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(transportation)) %>%
  compare_share(age_range, transportation)

transportation$kids_present <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(transportation)) %>%
  compare_share(kids_present, transportation)

food_barriers$transportation <- transportation %>%
  map(filter, transportation == "needed") %>%
  combine_dimensions(transportation)
```

```{r}
need_delivered <- list()
need_delivered$total <- fsrvys %>%
  map(filter, !is.na(current_food), !is.na(need_delivered)) %>%
  compare_share(total = "total", need_delivered)

need_delivered$by_gender <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(need_delivered)) %>%
  compare_share(gender, need_delivered)

need_delivered$by_race <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(need_delivered), race != "other") %>%
  compare_share(race, need_delivered)

need_delivered$by_age <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(need_delivered)) %>%
  compare_share(age_range, need_delivered)

need_delivered$kids_present <- fsrvys %>%
  map(filter, !is.na(freefood), !is.na(need_delivered)) %>%
  compare_share(kids_present, need_delivered)

food_barriers$need_delivered <- need_delivered %>%
  map(filter, need_delivered == "needed") %>%
  combine_dimensions(need_delivered)
```

```{r}
food_barriers$cant_afford %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(title = "couldn't afford food",
       caption = "of adults not having enough / desired food in past 7 days")
```

```{r}
food_barriers$transportation %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(title = "needed transportation to get food",
       caption = "of adults not having enough / desired food in past 7 days")
```

```{r}
food_barriers$need_delivered %>%
  filter(name == "CT" | dimension == "total") %>%
  compare_bars() +
  labs(title = "needed food delivered",
       caption = "of adults not having enough / desired food in past 7 days")
```


```{r}
saveRDS(food_sources, here::here("output_data/hhp_sources_of_food.rds"))
saveRDS(food_barriers, here::here("output_data/hhp_barriers_to_food.rds"))
```

